paper2_resistance_mechanisms_mixtures

### 2016-05-25 inst/documents/paper2_resistance_mechanisms_mixtures.Rmd
moved documents into own folder
edit text and start to look at single insecticide effects

### version 1

@@

We use a 2-locus population genetic model of insecticide resistance (Hastings et al. in press) to illustrate the mechanisms by which these parameters are expected to influence the development of insectide resistance under alternative insecticide use strategies. Hastings et al. (in press) describe the technical details of the model and explore large parameter ranges. In contrast we provide an accessible summary of the model and use selected parameter values to demonstrate the mechanisms by which different parameter values are expected to influence the development of resistance.

@@

*Before this add figures for effect of inputs on sole use.*

>>>>

### version 2

@@

We use a 2-locus population genetic model of insecticide resistance (Hastings et al. in press) to illustrate the mechanisms by which these parameters are expected to influence the development of insectide resistance under alternative insecticide use strategies. Hastings et al. (in press) describe the technical details of the model and explore large parameter ranges. In contrast we provide an accessible summary of the model and use selected parameter values to demonstrate mechanisms that can influence the development of resistance.

@@

*Before this add figures for effect of inputs on sole use.*
* contrasting pairs, or even 3 values, 0.1,0.5 & 0.9*
```{r, eval=TRUE, echo=FALSE, fig.height=4}

  #create empty object to hold input matrix for return
  #input <- NULL

  #??? but how do I set so just one insecticide ?
  #??? have I been doing this right in previous runs for this paper ?
  #??? maybe yes, because setExposure() is called from runcurtis_f2()
  #this sets exposures according to whether insecticide1,2 or mixture
  a <- setExposure(exposure=0.5, insecticideUsed='insecticide1')

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.2, 
                      h.RS2_0B = 0.2,
                      a = a,
                      phi.SS1_A0 = 0.2,
                      phi.SS2_0B = 0.2,
                      s.RR1_A0 = 0.2,
                      s.RR2_0B = 0.2 )

  i2 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      s.RR1_A0 = 0.5,
                      s.RR2_0B = 0.5 )

  #input <- cbind(input, inputOneScenario)
  input <- cbind(i1,i2)

  listOut <- runModel2( input )

  plotallele.freq.andy(listOut, locus="1", sex="mf_mean", add_legend=FALSE)

  cat("Fig. a1. starting to look at single insecticide effects")
```
